The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-23 manuscript/manuscript.Rnw
discuss pre-eclampsia genes

\DLA{Discuss pre-eclampsia specific genes here to make this point stronger}

@@

### Pre-eclampsia genes FSTL3 EPAS1 ADAM12 GPC3 TGFB1 PAPPA

>>>>

\paragraph{Pre-eclampsia \human Lineage Specific Genes}

Using a mixed-effects linear model to account for repeated testing of
\human and \mouse, we identified multiple genes which are
differentially expressed in the \human lineage in comparison to all
other lineages (\cref{tab:human_lineage_specific}). These genes
include multiple genes which are thought to be involved in
pre-eclampsia. Notably, \textit{CRH}
(FDR=\Sexpr{hum.all.lin.spec["CRH",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["CRH",`Fold Change`]}, Supplemental
\cref{fig:adam12_evolution_tree}), has been shown to be more highly
expressed in placentas from pre-eclamptic pregnancies
\cite{Petsas.ea2012:Aberrantexpressionofcorticotropin-releasing,Paiva.ea2011:MeasurementofmRNAtranscripts},
where it is hypothesized to activate decidual macrophages. Likewise,
\textit{KISS1} (\Sexpr{hum.all.lin.spec["KISS1",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["KISS1",`Fold Change`]}, Supplemental
\cref{fig:kiss1_evolution_tree}) also shows increased expression in
pre-eclamptic placentas
\cite{Vazquez-Alaniz.ea2011:Comparativeexpressionprofilesfor}, and is
involved in modulating trophoblast invasion. Two other genes,
\textit{PAPPA} (\Sexpr{hum.all.lin.spec["PAPPA",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["PAPPA",`Fold Change`]} Supplemental
\cref{fig:pappa_evolution_tree}) and \textit{ADAM12}
(\Sexpr{hum.all.lin.spec["ADAM12",`FDR`]},
FC=\Sexpr{hum.all.lin.spec["ADAM12",`Fold Change`]}, Supplemental
\cref{fig:adam12_evolution_tree}) are also differentially expressed
but are negatively correlated with pre-eclampsia
\cite{Spencer.ea2008:ADAM12sinmaternalserum}.

@@

### Pre-eclampsia genes ADAM12 CRH KISS1 PAPPA
